---
title: "iAdapt with nTTP under various hypotheses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = FALSE, warning = FALSE, message = FALSE)

source(file.path(getwd(), "nTTP_iAdapt-fns.R"))
library(tidyverse)
library(iAdapt)
load(file.path(getwd(), "scenarios.RData")) # data from Du et al
```

```{r}
p1 = c(0.30, 0.35, 0.40, 0.40) # unsafe nTTP (null hypothesis)
p2 = c(0.05, 0.10, 0.15, 0.10) # acceptable nTTP (alternative hypothesis)
sigma = 0.15 # variance of nTTP on each dose, assumed constant and estimated form simulated nTTP data
tru_tox = c(0.046, 0.054, 0.018, 0.183, 0.280, 0.359) # true (approx) nTTP for each dose, taken from Sumithra's paper

coh.size = 3 # number pts per dose
ntox <- 3 # Number of unique toxicities
d <- 6 # Number of dose levels
N <- 25 # maximum number of patients

# Efficacy(equal) variance per dose
v <- rep(0.01, 6) 

K = 2 # for LRT

sims = 1e3 # number of trials to simulate

#### Define the weight Matrix, from Sumithra's paper
W <- matrix(c(0.5, 0.75, 1.0, 1.5, # Burden weight for grades 1-4 for toxicity 1
              0.5, 0.75, 1.0, 1.5, # Burden weight for grades 1-4 for toxicity 2
              0.00, 0.00, 0.5, 1), ## Burden weight for grades 1-4 for toxicity 3
            nrow = ntox, byrow = T)

#### Define array to hold toxicitiy probabilities 
TOX <- array(NA, c(d, 5, ntox)) 

# Scenario 1 = from Du et al. paper
TOX[,,1] <- nTTP.matrix[4,1,1,1,,]

TOX[,,2] <- nTTP.matrix[4,1,2,1,,]

TOX[,,3] <- nTTP.matrix[4,1,3,1,,]

```


### Scenarios and nTTP hypotheses

Using the scenarios from Sumithra's paper, we have the following toxicity probabilities for grades 0-4 across 3 different toxicity types:

`r print(TOX)`

We also have the following weight matrix:

`r print(W)`

Here I simulate the iAdapt design 1000 times under different sets of nTTP hypotheses

* H0: p = 0.30 vs. H1: p = 0.05 (conservative)
* H0: p = 0.35 vs. H1: p = 0.10 (approximated from above weight matrix)
* H0: p = 0.40 vs. H1: p = 0.15 (Cody)
* H0: p = 0.40 vs. H1: p = 0.10 

We also have 5 dose-efficacy scenarios for the average nTTP across 6 doses: 

`r print(tru_tox)`

```{r, results=TRUE}
data.frame("Scenario 1" = c(10, 20, 30, 40, 70, 90),
           "Scenario 2" = c(50, 50, 50, 50, 50, 50),
           "Scenario 3" = c(20, 50, 80, 80, 80, 80),
           "Scenario 4" = c(80, 60, 40, 30, 20, 10),
           "Scenario 5" = c(30, 60, 80, 60, 30, 10)) %>%
  t %>%
  knitr::kable(col.names = paste("Dose", 1:6))
```


```{r scenario1}
# Vector of true mean efficacies per dose (here mean percent persistence per dose)
m1 <- c(10, 20, 30, 40, 70, 90)          
## Using nTTP
nTTP_1 <- lapply(1:length(p2), function(i){
  sim.trials.nTTP(numsims = sims,
                          dose = d,
                          p1 = p1[[i]],
                          p2 = p2[[i]],
                          K = K,
                          coh.size = coh.size,
                          m = m1,
                          v = v,
                          N = N,
                          W = W,
                          TOX = TOX,
                          ntox = ntox)
})
nTTP_1.pct_alloc = lapply(1:length(p2), function(i){
  sim.summary.new(nTTP_1[[i]], print = FALSE)
})

pct_alloc_table1 = do.call(rbind, lapply(nTTP_1.pct_alloc, function(i){
  i$pct.treated[, 5]
}))

```


```{r scenario2}
# Vector of true mean efficacies per dose (here mean percent persistence per dose)
m2 <- c(50, 50, 50, 50, 50, 50)   

## Using nTTP
## Using nTTP
nTTP_2 <- lapply(1:length(p2), function(i){
  sim.trials.nTTP(numsims = sims,
                          dose = d,
                          p1 = p1[[i]],
                          p2 = p2[[i]],
                          K = K,
                          coh.size = coh.size,
                          m = m2,
                          v = v,
                          N = N,
                          W = W,
                          TOX = TOX,
                          ntox = ntox)
})
nTTP_2.pct_alloc = lapply(1:length(p2), function(i){
  sim.summary.new(nTTP_2[[i]], print = FALSE)
})

pct_alloc_table2 = do.call(rbind, lapply(nTTP_2.pct_alloc, function(i){
  i$pct.treated[, 5]
}))

```

```{r scenario3}
# Vector of true mean efficacies per dose (here mean percent persistence per dose)
m3 <- c(20, 50, 80, 80, 80, 80)   # added last efficacy value for 6th dose   

## Using nTTP
nTTP_3 <- lapply(1:length(p2), function(i){
  sim.trials.nTTP(numsims = sims,
                          dose = d,
                          p1 = p1[[i]],
                          p2 = p2[[i]],
                          K = K,
                          coh.size = coh.size,
                          m = m3,
                          v = v,
                          N = N,
                          W = W,
                          TOX = TOX,
                          ntox = ntox)
})
nTTP_3.pct_alloc = lapply(1:length(p2), function(i){
  sim.summary.new(nTTP_3[[i]], print = FALSE)
})

pct_alloc_table3 = do.call(rbind, lapply(nTTP_3.pct_alloc, function(i){
  i$pct.treated[, 5]
}))
```

```{r scenario4}
# Vector of true mean efficacies per dose (here mean percent persistence per dose)
m4 <- c(80, 60, 40, 30, 20, 10)   # added last efficacy value for 6th dose      
## Using nTTP
nTTP_4 <- lapply(1:length(p2), function(i){
  sim.trials.nTTP(numsims = sims,
                          dose = d,
                          p1 = p1[[i]],
                          p2 = p2[[i]],
                          K = K,
                          coh.size = coh.size,
                          m = m4,
                          v = v,
                          N = N,
                          W = W,
                          TOX = TOX,
                          ntox = ntox)
})
nTTP_4.pct_alloc = lapply(1:length(p2), function(i){
  sim.summary.new(nTTP_4[[i]], print = FALSE)
})

pct_alloc_table4 = do.call(rbind, lapply(nTTP_4.pct_alloc, function(i){
  i$pct.treated[, 5]
}))

```

```{r scenario5}
# Vector of true mean efficacies per dose (here mean percent persistence per dose)
m5 <- c(30, 60, 80, 60, 30, 10)  

## Using nTTP
nTTP_5 <- lapply(1:length(p2), function(i){
  sim.trials.nTTP(numsims = sims,
                          dose = d,
                          p1 = p1[[i]],
                          p2 = p2[[i]],
                          K = K,
                          coh.size = coh.size,
                          m = m5,
                          v = v,
                          N = N,
                          W = W,
                          TOX = TOX,
                          ntox = ntox)
})
nTTP_5.pct_alloc = lapply(1:length(p2), function(i){
  sim.summary.new(nTTP_5[[i]], print = FALSE)
})

pct_alloc_table5 = do.call(rbind, lapply(nTTP_5.pct_alloc, function(i){
  i$pct.treated[, 5]
}))
```

Hypotheses:

Group 1: 0.30 vs 0.05 (conservative)

Group 2: 0.35 vs 0.10 (calculated from Ezzalfani weight matrix)

Group 3: 0.40 vs 0.15 (Cody)

Group 4: 0.40 vs 0.10

```{r result, results=TRUE}
# % of times dose is declared safe
pct_safe_table = do.call(rbind, lapply(nTTP_1, function(i){colMeans(i$safe.d)}))

rbind(
  tru_tox, 
  pct_safe_table
  ) %>%
  `rownames<-`(c(
    "True nTTP", 
    "P(safe) Group 1",
    "P(safe) Group 2",
    "P(safe) Group 3",
    "P(safe) Group 4"
    )) %>%
  knitr::kable(row.names = TRUE, 
               col.names = 1:6,
               caption = "Percent declared safe",
               format = "html") %>%
  kableExtra::kable_styling("striped", full_width = F) 

# % of times dose is declared safe
rbind(
  tru_tox, 
  m1,
  pct_alloc_table1,
  m2,
  pct_alloc_table2,
  m3,
  pct_alloc_table3,
  m4,
  pct_alloc_table4,
  m5,
  pct_alloc_table5
  ) %>%
  `rownames<-`(c(
    "True nTTP", 
    "True efficacy",
    "P(alloc) Group 1",
    "P(alloc) Group 2",
    "P(alloc) Group 3",
    "P(alloc) Group 4",
    "True efficacy",
    "P(alloc) Group 1",
    "P(alloc) Group 2",
    "P(alloc) Group 3",
    "P(alloc) Group 4",
    "True efficacy",
    "P(alloc) Group 1",
    "P(alloc) Group 2",
    "P(alloc) Group 3",
    "P(alloc) Group 4",
    "True efficacy",
    "P(alloc) Group 1",
    "P(alloc) Group 2",
    "P(alloc) Group 3",
    "P(alloc) Group 4",
    "True efficacy",
    "P(alloc) Group 1",
    "P(alloc) Group 2",
    "P(alloc) Group 3",
    "P(alloc) Group 4"
    )) %>%
  knitr::kable(row.names = TRUE, 
               col.names = 1:6,
               caption = "Average percent dose allocation",
               format = "html") %>%
  kableExtra::kable_styling("striped", full_width = F) %>%
  kableExtra::pack_rows("Scenario 1", 2, 6) %>%
  kableExtra::pack_rows("Scenario 2", 7, 11) %>%
  kableExtra::pack_rows("Scenario 3", 12, 16) %>%
  kableExtra::pack_rows("Scenario 4", 17, 21) %>%
  kableExtra::pack_rows("Scenario 5", 22, 26)


```

