---
title: "Building hypotheses for DLT rate comparable to nTTP"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = TRUE, warning = FALSE, message = FALSE)

source(file.path(getwd(), "nTTP_iAdapt-fns.R"))
library(tidyverse)
library(iAdapt)
load(file.path(getwd(), "scenarios.RData")) # data from Du et al
```

```{r}
p1 = 0.36 # unsafe nTTP (null hypothesis)
p2 = 0.17 # acceptable nTTP (alternative hypothesis)
sigma = 0.15 # variance of nTTP on each dose, assumed constant and estimated form simulated nTTP data
tru_tox = c(0.046, 0.054, 0.018, 0.183, 0.280, 0.359) # true (approx) nTTP for each dose, taken from simulations
DLT_rate = c(0.008, 0.011, 0.064, 0.195, 0.330, 0.446) # scenario equivalent for binary tox

coh.size = 3 # number pts per dose
ntox <- 3 # Number of unique toxicities
d <- 6 # Number of dose levels
N <- 25 # maximum number of patients

# Efficacy(equal) variance per dose
v <- rep(0.01, 6) 

K = 2 # for LRT

sims = 1e2 # number of trials to simulate

#### Define the weight Matrix
W <- matrix(c(0.5, 0.75, 1.0, 1.5, # Burden weight for grades 1-4 for toxicity 1
              0.5, 0.75, 1.0, 1.5, # Burden weight for grades 1-4 for toxicity 2
              0.00, 0.00, 0.5, 1), ## Burden weight for grades 1-4 for toxicity 3
            nrow = ntox, byrow = T)

#### Define array to hold toxicitiy probabilities 
TOX <- array(NA, c(d, 5, ntox)) 

# Scenario 1 = from Du et al. paper
TOX[,,1] <- nTTP.matrix[4,1,1,1,,]

TOX[,,2] <- nTTP.matrix[4,1,2,1,,]

TOX[,,3] <- nTTP.matrix[4,1,3,1,,]

```


### Scenarios and nTTP hypotheses

Using the scenarios from Sumithra's paper, we have the following toxicity probabilities for grades 0-4 across 3 different toxicity types:

```{r}
TOX
```


We also have the following weight matrix:

```{r}
W
```


From the weight matrix W, the nTTP hypotheses are computed as 

* H0: p = 0.36
* H1: p = 0.17


### Constructing comparable DLT hypotheses

Two possibilities:

1. H0: p = P(0 DLT) vs. H1: p = P(3 DLT), or
2. H0: p = P(0 or 1 DLT) vs. H1: p = P(2 or 3 DLT).

We can define P(x DLT) as 

$$P(x DLT) = \frac{\sum_{i = 1}^N \frac{\sum_{j = 1}^k P_{ij}(x DLT)}{k}}{N}$$

This averages the average P(x DLT) across $k$ doses, across $N$ toxicity types. 

```{r}
## all possible toxicity grades for each toxicity type
tox1 = tox2 = tox3 = 0:4
## grade that determines DLT for each toxicity type
tox_type.dlt_grade = c(3, 3, 4)

## dataframe of all possible combinations of grade levels across three toxicity types
tox.grid = expand.grid(tox1 = tox1, 
                       tox2 = tox2, 
                       tox3 = tox3)
## count number of DLTs for each combination
tox.grid = tox.grid %>%
  ## logical for whether grade meets DLT for given tox type
  mutate(tox1.dlt = if_else(tox1 >= tox_type.dlt_grade[[1]], 1, 0),
         tox2.dlt = if_else(tox2 >= tox_type.dlt_grade[[2]], 1, 0),
         tox3.dlt = if_else(tox3 >= tox_type.dlt_grade[[3]], 1, 0)) %>%
  rowwise %>%
  ## sum number of DLTs across tox types
  mutate(n.dlt = sum(tox1.dlt, tox2.dlt, tox3.dlt)) %>%
  arrange(n.dlt)

## dataframe average probability of each grade across all doses, for all toxicity types
grade.probs <- data.frame(tox = c(rep(1, 5), # toxicity type
                                  rep(2, 5),
                                  rep(3, 5)),
                          grade = rep(0:4, ntox), # grades
                          grade_prob = c(colMeans(TOX[,,1]), # average grade probs across all doses
                                         colMeans(TOX[,,2]),
                                         colMeans(TOX[,,3])))

## add ^ probabilities to tox.grid dataframe
tox.grid %>%
  ## match grade probs to given grade for given tox type
  left_join(., grade.probs[which(grade.probs$tox == 1), 2:3], by = c("tox1" = "grade")) %>%
  left_join(., grade.probs[which(grade.probs$tox == 2), 2:3], by = c("tox2" = "grade")) %>% 
  left_join(., grade.probs[which(grade.probs$tox == 3), 2:3], by = c("tox3" = "grade")) %>% 
  ## calculate average prob of grade combo
  rowwise %>%
  mutate(avg.prob = mean(c(grade_prob.x, grade_prob.y, grade_prob))) %>% 
  ## calculate average prob of number of dlts
  group_by(n.dlt) %>%
  summarise(p_n.dlt = mean(avg.prob))
```

So we have: 

1. H0: p = 0.29 vs H1: p = 0.05
2. H0: p = 0.49 vs H1: p = 0.17
